Reporte de inventario de eviencias

### 2021-10-12 Latex/journal_v1/research plan/main.tex
research plan change

\pagebreak
\begin{abstract}
Open radio access network (O-RAN) is the next generation of RAN systems introduced by the O-RAN Alliance to increase the flexibility and the openness of the network systems and simultaneously decrease CAPEX and OPEX of mobile operators. The O-RAN system combines and takes advantage of Cloud RAN (C-RAN) and the Virtual RAN (VRAN).
O-RAN separates RAN into three
different units, namely Radio Unit (O-RU), Distributed Unit
(O-DU), and Central Unit (O-CU).
In this research, we study
the problem of baseband resource allocation and virtual
network function (VNF) activation in O-RAN architecture
based on their service priority for different types of 5G services
including enhanced mobile broadband (eMBB), ultra-reliable
low latency communications (uRLLC) and massive Machine
Type Communications (mMTC) services using intelligent RAN slicing. 
Network slicing is a promising solution for supporting such heterogeneous and challenging services.
Deploying network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed. The limited
fronthaul capacity, the restriction of end-to-end delay and the reliability of the services are
considered at the same time.

The optimization of baseband
resources includes O-RU assignment, the assignment of physical resource block
(PRB), and power allocation. The main problem is a mixed-integer non-linear programming problem that is tremendously difficult. Since the problem has a two-time scale, it can be broken into two layers. On the large-time scale, the problem of obtaining the optimal number of VNF, the placement of VNFs, and the assignment of PRB to the slices are considered. 
On the small-time scale, there is a problem of obtaining the optimal power of UEs, and the PRB and O-RU assignment.
To solve the problem, we propose deep reinforcement learning, the deep deterministic policy gradient (DDPG) method, and convex optimization.
\end{abstract}
\section{Introduction} 
O-RAN, as the integration and expansion of C-RAN and xRAN, or C-RAN and vRAN is expected to be a key technology in 5G networks to enhance the RAN performance extensively. 
The core idea of C-RAN is to divide the radio remote head (RRU) from the baseband unit (BBU). Also, several BBUs are placed together to create the BBU-pool, providing unified baseband signal processing with powerful computing capabilities. On the other hand, xRAN technology has three fundamental features. The control plane is decoupled from the user plane. Besides, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware. Moreover, open north-bound and south-bound interfaces are introduced.
O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU). O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node that includes higher PHY, MAC, and RLC. In addition, the O-CU depicts the logical node contains two parts, which are the O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC. O-DU and O-CU are connected via an open and well-defined interface F1.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation,
RAN Intelligent Controller (RIC)- Near Real-Time and O-Cloud. 
One of the necessities of the new generation of wireless networks is its intelligence.
Based on the requirement of an intelligent wireless network, O-RAN offers machine learning techniques. The two logical nodes RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC- Near Real Time, implement the algorithms for network intelligence 
\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
\begin{figure*}
  \centering 
    \includegraphics[scale = 0.5]{finalDraw.pdf}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure*}

One of the goals of the next generation of mobile systems is to strictly meet the stringent QoS demands of the different services introduced in 5G , i.e., eMBB, URLLC, and mMTC. Network slicing is a promising solution to obtain the QoS for each type of service. Network slicing contains RAN slicing, core slicing, and both of them together. Efficient slicing of RAN is still challenging due to time-varying network circumstances.
%Network slicing will propose significant complexity into the performance of systems that causes conventional mathematical model-based procedures to network operation no longer adequate. 
Network slicing creates considerable complexity in system performance and makes the conventional mathematical methods insufficient to model the network.
Therefore, it motivates researchers to realize network slicing using machine learning strategies such as deep learning and deep reinforcement learning. So, the network can reach the best control policy according to its experience in the past time slots.
As mentioned above, network slicing, which contains RAN slicing, core slicing, and the whole, is considered a hot topic for vendors. In addition, the O-RAN system seems to be the next RAN architecture. So, this motivated researchers to study the dynamic RAN slicing in O-RAN architecture to achieve the desired QoS for each service type.
In addition, according to the high complexity of RAN slicing and incapability of the traditional model-based methods, dynamic machine learning becomes the best solution for these problems.
 Generally, there are two kinds of deep reinforcement learning methods for solving dynamic problems. The first class is value-based such as Deep-Q-Network, and the second class is policy-based problems such as DDPG. The first class can only solve the discrete action space problems, which are integer programming. The second class can solve by searching the optimal policy, which is the actor-critic method. Here, we use the second method to solve our problems \cite{alsenwi2021intelligent,yan2019intelligent,mei2021intelligent}.
\subsection{Related Works} 
In \cite{mei2021intelligent}, the authors proposes a new intelligent RAN slicing method with two-layered control granularity, which aims at maximizing both the long-term QoS of services and spectrum efficiency (SE) of slices. In this paper, the authors design a RAN slicing strategy with multiple time and
resource granularities to accommodate the time-varying network conditions and diverse QoS requirements.
Here, the DDPG method is applied for the lower level and deep Q-network is applied for upper level.

In paper \cite{rezazadeh2021actor}, an actor-critic methods and a continuous model-free deep reinforcement
learning (DRL) method is applied to minimize energy consumption and virtual network function (VNF) instantiation cost.
Multiplexing eMBB and uRLLC services on the same RAN and sharing the resources of these services is challenging, and many researchers pay attention to this issue.
In \cite{setayesh2020joint,yang2020should}, the problem of resource allocation in the coexistence of URLLC and eMBB services is considered based on their QoS. 
Paper \cite{alsenwi2021intelligent}, represents a joint convex method and deep reinforcement learning to schedule both eMBB and URLLC services. Here we have two time-scale, a two-phase-framework, including eMBB resource allocation and URLLC scheduling phases.  
In \cite{saggese2021power}, the problem of power minimization for uRLLC and eMBB services is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA).
 In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in coexistence of eMBB and URLLC services. The system guarantees the latency, the service rate, and the maintenance of reliability.

\subsection{Main Contributions}
In this research, as depicted in Figure \ref{fig:c11}, we aim at solving the problem of dynamic network slicing in the O-RAN system. 
Here, we study a single-cell downlink situation involving multiple network slices that share existing radio sources.
The main contributions of
this research are summarized as follow:
\begin{itemize}
\item 
The system has a two-time scale and should be solved in two layers. On a large-time scale, the problem of obtaining an optimal number of VNFs and the VNF placement is performed. Also, the assignment of PRB to the slices is obtained. On a small-time scale, the problem of power allocation, O-RU association and the assignment of PRB to UE in each slice is applied.
\item 
In this research, we consider three types of services that requires specific QoS: URLLC, which requires low latency and high reliability; eMBB, which needs high data rate; and mMTC, that are massive devices with short packets and low power devices.
The problem of RAN slicing for different types of services is studied in this research.

\item 
In this research, we consider an intelligent resource allocation in the O-RAN architecture for the different scenarios of services. Since, the conventional models cannot perform well in the system because of the different QoS for each service type, and the complexity of dynamic RAN slicing. So we must switch to machine learning and dynamic methods and find the most suitable approach.  
A dynamic strategy of resource allocation is required to solve this problem to achieve the specific QoS for each type of service in the O-RAN architecture.
 In the small-time scale, the actor-critic algorithm such as DDPG is applied to the system that is based on control policy search. This method directly searches the optimal control policy
by estimating of the gradient with respect to the parameters
of the control policy. In the large-time scale, the deep reinforcement learning is implemented which is a value based algorithm.
\item 
Also, another goal of this project is to apply transfer learning to the system and enhance the performance and the convergence of the methods. 
\end{itemize}
\section{System Model}
In this section, first, we  present the system model. Then, we obtain achievable data rates and delays for the downlink (DL) of the ORAN system. Afterward, we discuss about assignment of physical data center resources.
Finally, the main problem is expressed.
\subsection{System Model}
Suppose we have three service types includes eMBB, URLLC, and mMTC. Assume we have $S_1$, $S_2$, and $S_3$ different applications for the first, second and third service type, respectively ($S = S_1 + S_2 +S_3$).
Assume we have $S$ preallocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
Each Service $s_j\in \{1,2,...,S_j \} $ consists of $U_{s_j}$ request from the 
single-antenna UEs which require certain QoS to be able to use the requested program($j \in \{1,2,3\}$ indicate service type).
There are different application request which fall into one of these service categories. Each application request requires specific QoS. Based on the request for the application and QoS, UE may be admitted and allocated to the resources.
Assume each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of $K_{s_j}$, $j \in \{1,2,3\}$ pre-allocated physical resource blocks (PRBs) that obtained in the large-time scale, $M_s^{d}$ VNFs for the processing of O-DU,  $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.

Also, each VNF instance is running on the virtual machine (VM) that are using resources from the data centers. Each VM, requires enough resources of CPU, memory, storage and network bandwidth.

In addition, there are $R$ multi-antenna RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data. Moreover, all RUs, have access to PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE requesting served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq2}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
\end{equation}
Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE allocate to $s^{th}$ slice or not. 
Also, $BN_0$ denotes the power of Gaussian additive noise.
Also, $a_{u(s,i)} \in \{0,1\}$ is a binary variable to depict user admission.
$e^{k}_{r,u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.

The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}^{e}$.
\begin{equation}\label{eq1}
\begin{split}
\mathcal{R}_{u(s_1,i)}^{e,r} &= \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},\\
\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r} 
\end{split}
\end{equation}
where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th} $, $j \in \{2,3\}$ application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula. So, for the short packet transmission the achievable data rate is approximated from follow
\begin{equation}\label{eq11}
\begin{split}
\mathcal{R}_{u(s_2,i)}^{\mathfrak{u},r} &= \sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_2,i)}^{k}){\beta}_{u(s_2,i)}^{k}, \quad \mathfrak{u} \in  \{u,m\} \\
\mathcal{R}_{u(s_1,i)}^{\mathfrak{u}} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_2,i)}^{e,r} 
\end{split}
\end{equation}
Where ${\beta}_{u(s_2,i)}^{k}=a_{u(s_2,i)} e^{k}_{u(s_2,i)}$
and $\zeta_{u(s_2,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_2,i)}^{k}}{N_{u(s_2,i)}^{k}}})$
Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
$C_{u(s_2,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_2,i)}^{k})}$ depicts the channel dispersion of UE  $i$ at slice $s_2$, experiencing PRB $k$ and
$N_{u(s_2,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_2$.
\subsection{Mean Delay}
In this part, the end to end mean delay for a service is obtained.
Suppose the mean total delay is depicted as $T_{tot}$.
\begin{equation}
\begin{split}
T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
\end{split}
\end{equation}
%T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
Total delay is sum of processing delay, transmission delay and propagation delay. 
The propagation delay is the time takes for a signal to reach to its destination. So it has a constant value based on the length of fiber link ($T = L/C_{r}$, where $L$ is the length of link and $C_{r}$ is the capacity of the link).
Here we assume the value of propagation delay is negligible compared to the rest.
\subsubsection{Processing Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ slice.
Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^1 = \sum_{u=1}^{U_s}a_{u(s,i)}\lambda_{u(s,i)}$, where $a_{u(s,i)}$ is a binary variable which indicates whether the $i^{th}$ UE requested $s^{th}$ service is admitted or not.

Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. since, by using Burke’s Theorem, the mean arrival data rate of the second and third layer which are processed in the first layer is still Poisson with rate $\alpha_{s}$.
It is assumed that there are load balancers in each layer for each service to divide the incoming traffic to VNFs equally. %\cite{frdl,luong2018novel,luong2018novel1}.
Suppose the baseband processing of each VNF is depicted as M/M/1 processing queue.
Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the first and the second layer, modeled as M/M/1 queue, is formulated as follow, respectively
\begin{equation}
\begin{split}
T_{DU}^{s} &= \frac{1}{\mu_d - \alpha_{s}/{M_s^{d}}},\\
T_{CU}^{s} &= \frac{1}{\mu_c - \alpha_{s}/{M_s^{c}}}\\
T_{UPF}^{s} &= \frac{1}{\mu_u - \alpha_{s}/{M_s^{u}}}\\
\end{split}
\end{equation}
Where $M_s^{d}$, $M_s^{c}$ and 
$M_s{u}$ are the variables that depict the sum of VNFs in O-DU, O-CU-UP and UPF, respectively. 
Moreover, $1/\mu_d$, $1/\mu_c$ and $1/\mu_u$ are the mean service time of the O-DU, O-CU and the UPF layers respectively.
Besides, $\alpha_{s}$ is the  arrival rate which is divided
by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for each slice 
$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c, u\}$.

In addition, $T_{RU}^{s}$ is the mean transmission delay of $s^{th}$ slice on the wireless link. The arrival data rate of wireless link is equal to the arrival data rate of load balancers for each service.
 %\cite{frdl}.
Moreover, it is assumed that the service time of transmission queue for each slice $s$ has
 an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue.
 %\cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. 
 Therefore,
the mean delay of the transmission layer is
 T_{RU}^{s} = \frac{1}{R_{{tot}_s} - \alpha_{s}};

@@

where, $R_{{tot}_s} = \sum_{u=1}^{U_s}a_{u(s,i)}R_{u(s,i)}$ is the total achievable rate of each service.
So the mean processing delay for each UE in slice $s$ is 
T_{process}^{s} =  T_{RU}^{s} + T_{DU}^{s} + T_{CU}^{s} + T_{UPF}^{s}

@@

\subsubsection{Transmission Delay}
The transmission delay is the amount of time required to push all the packets into the fiber link. 
Here, we have transmission delay in fronthaul, midhaul, backhaul and the link to transmit data to internet.

@@

physical resources that contain memory, storage, CPU and Network Bandwidth.

>>>>

\pagebreak
\begin{abstract}
Open radio access network (O-RAN) is the next generation of RAN systems introduced by the O-RAN Alliance to increase the flexibility and the openness of the network systems and simultaneously decrease CAPEX and OPEX of mobile operators. The O-RAN system combines and takes advantage of Cloud RAN (C-RAN) and the Virtual RAN (VRAN).
O-RAN separates RAN into three
different units, namely Radio Unit (O-RU), Distributed Unit
(O-DU), and Central Unit (O-CU).
In this research, we study
the problem of baseband resource allocation and virtual
network function (VNF) activation in O-RAN architecture
based on their service priority for different types of 5G services
including enhanced mobile broadband (eMBB), ultra-reliable
low latency communications (uRLLC) and massive Machine
Type Communications (mMTC) services using intelligent RAN slicing. 
Network slicing is a promising solution for supporting such heterogeneous and challenging services.
Deploying network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed. The limited
fronthaul capacity, the restriction of end-to-end delay and the reliability of the services are
considered at the same time.
The optimization of baseband
resources includes O-RU assignment, the assignment of physical resource blocks
(PRBs), and power allocation. The main problem is a mixed-integer non-linear programming problem that is tremendously difficult. Since the problem has a two-time scale, it can be broken into two layers. On the large-time scale, the problem of obtaining the optimal number of VNF, the placement of VNFs, and the assignment of PRB to the slices are considered. 
On the small-time scale, there is a problem of obtaining the optimal power of UEs, and the PRB and O-RU assignment.
To solve the problem, we propose deep reinforcement learning, the deep deterministic policy gradient (DDPG) method, and convex optimization.
\end{abstract}
\section{Introduction} 
Open radio access network (O-RAN), as the integration and expansion of cloud RAN (C-RAN) and xRAN, or C-RAN and virtual RAN (vRAN), is expected to be a key technology in 5G networks to enhance the RAN performance extensively. 
The core idea of C-RAN is to divide the radio remote head (RRU) from the baseband unit (BBU). Also, several BBUs are placed together to create the BBU-pool, providing unified baseband signal processing with powerful computing capabilities. On the other hand, xRAN technology has three fundamental features. The control plane is decoupled from the user plane. Besides, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware. Moreover, open north-bound and south-bound interfaces are introduced.
O-RAN, as illustrated in Fig. \ref{fig:c11}, separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU). O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node that includes higher PHY, MAC, and RLC. In addition, the O-CU depicts the logical node contains two parts: the O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC. O-DU and O-CU are connected via an open and well-defined interface F1.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation,
RAN Intelligent Controller (RIC)- Near Real-Time and O-Cloud. 
One of the necessities of the new generation of wireless networks is its intelligence.
Based on the requirement of an intelligent wireless network, O-RAN offers machine learning techniques. The two logical nodes RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC- Near Real-Time, implement the algorithms for network intelligence
\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.
\begin{figure*}
  \centering 
    \includegraphics[scale = 0.5]{finalDraw.pdf}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure*}

One of the goals of the next generation of mobile systems is to strictly meet the stringent QoS demands of the different services introduced in 5G , i.e., eMBB, URLLC, and mMTC. Network slicing is a promising solution to obtain the QoS for each type of service. Network slicing contains RAN slicing, core slicing, and both of them together. Efficient slicing of RAN is still challenging due to time-varying network circumstances.
%Network slicing will propose significant complexity into the performance of systems that causes conventional mathematical model-based procedures to network operation no longer adequate. 
Network slicing creates considerable complexity in system performance and makes the conventional mathematical methods insufficient to model the network.
Therefore, it motivates researchers to realize network slicing using machine learning strategies such as deep learning and deep reinforcement learning. So, the network can reach the best control policy according to its experience in the past time slots.
As mentioned above, network slicing, which contains RAN slicing, core slicing, and the whole, is considered a hot topic for vendors. In addition, the O-RAN system seems to be the next RAN architecture. So, this motivated researchers to study the dynamic RAN slicing in O-RAN architecture to achieve the desired QoS for each service type.
In addition, according to the high complexity of RAN slicing and incapability of the traditional model-based methods, dynamic machine learning becomes the best solution for these problems.
 Generally, there are two kinds of deep reinforcement learning methods for solving dynamic problems. The first class is value-based such as Deep-Q-Network, and the second class is policy-based problems such as
deep deterministic policy gradient (DDPG). The first class can only solve the discrete action space problems, which are integer programming. The second class can solve by searching the optimal policy, which is the actor-critic method. Here, we use the second method to solve our problems \cite{alsenwi2021intelligent,yan2019intelligent,mei2021intelligent}.
\subsection{Related Works} 
In \cite{mei2021intelligent}, the authors proposes a new intelligent RAN slicing method with two-layered control granularity, which aims at maximizing both the long-term QoS of services and spectrum efficiency (SE) of slices. In this paper, the authors design a RAN slicing strategy with multiple time and
resource granularities to accommodate the time-varying network conditions and diverse QoS requirements.
Here, the DDPG method is applied for the lower level and deep Q-network is applied for upper level.
In paper \cite{rezazadeh2021actor}, an actor-critic methods and a continuous model-free deep reinforcement
learning (DRL) method is applied to minimize energy consumption and virtual network function (VNF) instantiation cost.
Multiplexing eMBB and uRLLC services on the same RAN and sharing the resources of these services is challenging, and many researchers pay attention to this issue.
In \cite{setayesh2020joint,yang2020should}, the problem of resource allocation in the coexistence of URLLC and eMBB services is considered based on their QoS. 
Paper \cite{alsenwi2021intelligent}, represents a joint convex method and deep reinforcement learning to schedule both eMBB and URLLC services. Here we have two time-scale, a two-phase-framework, including eMBB resource allocation and URLLC scheduling phases.  
In \cite{saggese2021power}, the problem of power minimization for uRLLC and eMBB services is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA).
 In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in coexistence of eMBB and URLLC services. The system guarantees the latency, the service rate, and the maintenance of reliability.

\subsection{Main Contributions}
In this research, as depicted in Figure \ref{fig:c11}, we aim at solving the problem of dynamic network slicing in the O-RAN system. 
Here, we study a single-cell downlink situation involving multiple network slices that share existing radio sources.
The main contributions of
this research are summarized as follow:
\begin{itemize}
\item 
The system has a two-time scale and should be solved in two layers. On a large-time scale, the problem of obtaining an optimal number of VNFs and the VNF placement is performed. Also, the assignment of PRB to the slices is obtained. On a small-time scale, the problem of power allocation, O-RU association and the assignment of PRB to UE in each slice is applied.
\item 
We consider three types of services that requires specific QoS: URLLC, which requires low latency and high reliability; eMBB, which needs high data rate; and mMTC, , which demand short-packet connectivity support for a massive number of low-power devices.
The problem of RAN slicing for different types of services is studied in this research.

\item 
We consider an intelligent resource allocation in the O-RAN architecture for the different services. Since conventional models do not perform well here because of the heterogeneous QoS requirements of each service type and the complexity of dynamic RAN slicing. So we must switch to machine learning and dynamic methods and find the most suitable approach.  
A dynamic strategy of resource allocation is required to solve this problem to achieve the specific QoS for each type of service in the O-RAN architecture.
 In the small-time scale, the actor-critic algorithm such as DDPG is applied to the system that is based on control policy search. This method directly searches the optimal control policy
by estimating of the gradient with respect to the parameters
of the control policy. In the large-time scale, the deep Q-Network is implemented which is a value based algorithm and it can find best solution for discrete action-state.
\item 
We aim to apply transfer learning to the system and study the enhancement of performance and convergence. We can use Q-value transfer learning and action-selection transfer learning, So agents can utilize the knowledge of experts to improve their performance on current tasks\cite{zhou2021learning}. 
\end{itemize}
\section{Current State of the Research}
\subsection{System Model}
Assume we have $S$ preallocated slices serving $S$ services contains eMBB, URLLC, and mMTC services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC), , thus $S=S_1+S_2+S_3$.
Each Service $s\in \{1,2,...,S\} $ consists of $U_{s}$ single-antenna user equipments (UEs) which require certain QoS to be able to use the requested program.
There are different application requests which fall into one of these service categories. Each application request requires specific QoS. Based on the request for the application and QoS, a UE may be admitted and allocated to the resources.
Assume each slice $s \in \{1,2,...,S \}$, consists of $K_{s}$, pre-allocated physical resource blocks (PRBs)  obtained in the large-time scale, $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF. 
Virtual network functions (VNFs) are functional blocks of the
system. Each VNF instance is running on a virtual machine (VM) using resources from the data centers. Each VM, requires enough resources of CPU, memory, storage and network bandwidth.

In addition, there are $R$ multi-antenna RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data. Moreover, all RUs, have access to PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE requesting served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq2}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2}{BN_0 + I_{r,u(s,i)}^{k}},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
\end{equation}
Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE allocated to $s^{th}$ slice or not. 
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
\begin{equation}\label{eqI}
\begin{split}
I_{r,u(s,i)}^{k} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{split}
\end{equation}
where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.

The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}^{e}$.
\begin{equation}\label{eq1}
\mathcal{R}_{u(s_1,i)}^{e,r} &= \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},\\
\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r} 

@@

where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th} $, $j \in \{2,3\}$ application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula. So, for the short packet transmission the achievable data rate is approximated as follow
\begin{equation}\label{eq11}
\mathcal{R}_{u(s_2,i)}^{\mathfrak{u},r} &= \sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_2,i)}^{k}){\beta}_{u(s_2,i)}^{k}, \quad \mathfrak{u} \in  \{u,m\} \\
\mathcal{R}_{u(s_1,i)}^{\mathfrak{u}} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_2,i)}^{e,r} 

@@

where ${\beta}_{u(s_2,i)}^{k}=a_{u(s_2,i)} e^{k}_{u(s_2,i)}$
and $\zeta_{u(s_2,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_2,i)}^{k}}{N_{u(s_2,i)}^{k}}})$
where $\epsilon$ is the transmission error probability, $Q^{-1}$ is the inverse of Q function (i.e., Gaussian),
$C_{u(s_2,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_2,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_2$, experiencing PRB $k$ and
$N_{u(s_2,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_2$.
\subsection{Mean Delay}
In this part, the end-to-end mean delay for each service is obtained.
Suppose the mean total delay is depicted as $T_{\text{\text{tot}}}$,

@@

physical resources that include memory, storage, CPU and Network Bandwidth.
